\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}


\title{Your Paper}
\author{You}

\begin{document}
\maketitle

\pagebreak


\section{Introduction}

In Bangladesh almost every fashion brand is Dhaka or urban centric. That's why they can reach only a little margin of people throughout the country. The brands are already renowned with their product quality in offline market. But to extend their business it needs a huge investment and also it is too hard to reach every people all over Bangladesh. So, e-commerce is the suitable option for fashion brands to extend their business. This web application will contain all products information with picture so that customer can understand every parameter of that product. Then they can add product to the cart/Wishlist as well as they can place their order. The merchant will get those order and will supply good throughout the country from one area. Again, the customer will able to see current stage of their order within website.



\section{Objective}

\begin{enumerate}
\item Like this,
\item and like this.
\end{enumerate}



\section{Target Customers}
As this is an e-commerce site Our targeted customers are almost anyone in the society.
\begin{enumerate}
\item Male
\item Female
\item Kids
\end{enumerate} 

\begin{itemize}
\item Like this,
\item and like this.
\end{itemize}


\section{Value Proposition}

\subsection{Eliminates Inventory Cost}
One of the biggest drawbacks of running an offline retail business is it needs a lot of inventory cost. But in e-commerce the merchant can deliver their product from their warehouse. Thus, inventory cost eliminates. 

\subsection{Lower Costs}
In e-commerce the merchant can sell the product with less employee and less place. Which obviously reduce cost maximize the profit and the gets enough room to give offer to their customers so that they will buy more. 

\subsection{Flexibility}
One customer can buy goods from anywhere they want. The customers no need to go out and find some times for shopping. They can order and get delivery to their home.



\section{Web Application Feature and description}

This is a basic idea of features that our customers will have in the website. Customers have to create an account to use most of the features. Once they created an account: They can place order Add products in wish list. will get Recommended suggestions. Rate and Review Shops/Products. Access history of their past purchases. Notifications for sale, Product Arrival

\section{Tools and Resources}
\begin{itemize}
\item HTML
\item JavaScript
\item MySQL
\item PHP
\item Web server
\item API for SMS
\end{itemize}


\section{Challenge}
The web application needs to be user friendly so that every age or types of people can understands the way of finding and buying stuffs. There are huge numbers of products in a fashion brand. It is quite difficult to show all the products section by section in a simple way.  Again, for advance payment the security of online payment will be difficult task.


\end{document}
